Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-11-19 Ch1_movement_rates/Ch1_Figures.Rmd
Still working on the results figures

cp.summ.df %>%
  dplyr::select(av.disp, dsprsn, model) %>% 
  bind_rows(., pp.summ.df %>%
              dplyr::select(av.disp, dsprsn, model)) %>%
  bind_rows(., np.summ.df %>%
              dplyr::select(av.disp, dsprsn,  model)) %>% 
  mutate(model = factor(model, levels = c("cp", "pp","np"))) -> disp_df
```

@@

Importance of the outliers here

```{r}
disp_df %>%
  group_by(., model) %>%
  #sample_n(., 5000) %>%
  ggplot(., aes(y = dsprsn, x = model)) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  labs(title = "Dispersion", y = "Dispersion in meters", x = "Model") +
  theme_bw() +
  theme(legend.position = "none") -> p_dispersion

disp_df %>%
  group_by(., model) %>%
  #sample_n(., 5000) %>%
  ggplot(., aes(y = av.disp, x = model)) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  labs(title = "Average dispersal", y = "Dispersal in meters", x = "Model") +
  theme_bw() +
  theme(legend.position = "none") -> p_dispersal

@@

# Idea for dispersal and dispersion
Too many points, since we have 500k seeds, take 2%

```{r fig.height=12}

points_plot <- function(seed.data, s.size = 1000, xylims=1250, lalpha = 0.3){
  seed.data %>% 
    drop_na(s.id) %>% 
    mutate(ov500 = ifelse(disp <500, "non", "ldd")) %>% 
    sample_n(s.size) %>% 
      ggplot(., aes(x = xloc, y = yloc, color = ov500)) +
      geom_point(alpha = lalpha) +
      coord_equal(xlim = c(-xylims, xylims), ylim = c(-xylims, xylims)) +
      theme_bw()

}

A <- points_plot(seed.data = cp.df)
B <- points_plot(seed.data = pp.df)
C <- points_plot(seed.data = np.df)

plot_grid(A, B, C, nrow = 3)

>>>>

cp.summ.df %>%
  dplyr::select(av.disp, dsprsn, model) %>% 
  bind_rows(., pp.summ.df %>%
              dplyr::select(av.disp, dsprsn, model)) %>%
  bind_rows(., np.summ.df %>%
              dplyr::select(av.disp, dsprsn,  model)) %>% 
  mutate(model = toupper(model),
         model = factor(model, levels = c("CP", "PP","NP"))) -> disp_df
```

@@

Build a table with quantiles or summary stats for the dispersal and dispersion per run. Dispersion tells us how spread appart the seeds are from each other during a simulation. I would expect that for individuals with higher movement rates dispersion might be higher for their simulation runs too. This because a higher movement rate would extend the tail of the exponential distribution for movement distances, and thus have a larger range for movement distances, with a higher probability larger movement distances. So, during a simulation, a bird would see itself taking larger steps if they have a larger movement rate. Thus, their seeds would potentially be distributed more far apart.

```{r}
disp_df %>% 
  group_by(model) %>% 
  summarise(av.disp = round(quantile(av.disp, c(0, 0.25, 0.5, 0.75, 0.9, 1)), digits = 1),
            dsprsn = round(quantile(dsprsn, c(0, 0.25, 0.5, 0.75, 0.9, 1)),digits = 1),
            q = c("min", 0.25, 0.5, 0.75, 0.9, "max")) %>% 
  pivot_longer(cols = c(av.disp, dsprsn), names_to = "property", values_to = "value") %>% 
  pivot_wider(., names_from = q, values_from = value) %>% 
  arrange(., property) -> qtable_models

qtable_models
```

### Idea for dispersal and dispersion

Too many points, since we have 500k seeds, show only a percentage.

```{r fig.width=9, fig.height=3.5}

points_plot <- function(seed.data, summ.data, s.size = 1000, xylims=1250, lalpha = 0.5, scenario = NULL){

  seed.data %>% 
    drop_na(s.id) %>% 
    mutate(dispcat = ifelse(disp <500, "non", "ldd")) %>% 
    #slice_head(., n = s.size) %>% 
    sample_n(s.size) %>% 
      ggplot(., aes(x = xloc, y = yloc, color = dispcat)) +
      geom_point(alpha = lalpha) +
      labs(subtitle = scenario) +
      scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
      coord_equal(xlim = c(-xylims, xylims), ylim = c(-xylims, xylims)) +
      theme_bw() +
      theme(legend.position = "none",
            axis.title = element_blank()) +
       NULL -> seedlocplot

  # summ.data %>%
  #   #cp.summ.df %>%
  #   sample_n(s.size) %>%
  #   #slice_head(., n = s.size/5) %>%
  #   #pivot_longer(., cols = c(dsprsn, av.disp)) %>%
  #   #ggplot(., aes(x = name, y = value)) +
  #   ggplot(., aes(y = dsprsn)) +
  #   #geom_violin() +
  #   #geom_jitter(position = position_jitter(0.1), alpha = lalpha) +
  #   geom_boxplot(width = 0.1) +
  #   #geom_point(aes(x=0, color = run)) +
  #   lims(y = c(0, 650)) +
  #   labs(y = "Dispersion in meters") +
  #   theme_bw() +
  #   NULL -> dispersionplot
  # 
  # summ.data %>%
  #   #cp.summ.df %>%
  #   sample_n(s.size) %>%
  #   #slice_head(., n = s.size/5) %>%
  #   #pivot_longer(., cols = c(dsprsn, av.disp)) %>%
  #   #ggplot(., aes(x = name, y = value)) +
  #   ggplot(., aes(y = av.disp)) +
  #   #geom_violin() +
  #   #geom_jitter(position = position_jitter(0.1), alpha = lalpha) +
  #   geom_boxplot(width = 0.1) +
  #   #geom_point(aes(x=0, color = run)) +
  #   lims(y = c(0, 1300)) +
  #   labs(y = "Dispersal in meters") +
  #   theme_bw() +
  #   NULL -> dispersalplot
  # 
  # plot_grid(seedlocplot, dispersalplot, dispersionplot, ncol=3, rel_widths = c(2,1,1))
  # 
}

A <- points_plot(seed.data = cp.df, summ.data = cp.summ.df, scenario = "CP")

#A

B <- points_plot(seed.data = pp.df, summ.data = pp.summ.df, scenario = "PP")
C <- points_plot(seed.data = np.df, summ.data = np.summ.df, scenario = "NP")

seedplots2d <- plot_grid(A, B, C, ncol = 3)

```{r fig.width=9, fig.height=4}

disp_df %>%
  group_by(., model) %>%
  sample_n(., 50000) %>%
  #mutate(dispcat = ifelse(disp <500, "non", "ldd")) %>%
  ggplot(., aes(y = dsprsn, x = model)) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  #scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
  labs(y = "Dispersion in meters") +
  theme_bw() +
  theme(legend.position = "none",
        axis.title = element_blank()) -> p_dispersion

disp_df %>%
  group_by(., model) %>%
  sample_n(., 50000) %>%
  mutate(dispcat = ifelse(av.disp <500, "non", "ldd")) %>%
  ggplot(., aes(y = av.disp, x = model, color = dispcat)) +
  geom_boxplot() +
  geom_point(color = "grey", alpha = 0.5) +
  scale_color_manual(values = c(my.cols1[6], my.cols1[7])) +
  labs(y = "Average dispersal in meters") +
  theme_bw() +
  theme(legend.position = "none",
        axis.title = element_blank()) -> p_dispersal

@@

```{r}
cp.df %>% 
  drop_na(s.id) %>% 
  left_join(., cp.summ.df) -> testdata

testdata %>% 
  sample_n(1000) %>% 
  ggplot(., aes(x = xloc, y = yloc, color = dsprsn)) +
  geom_point() +
  scale_color_viridis_c(direction = -1) +
  theme_bw()

cp.summ.df %>% 
  sample_n(1000) %>% 
  ggplot(., aes(y = dsprsn, x = av.disp)) +
  geom_point()

cp.summ.df %>% 
  sample_n(100) %>% 
  ggplot(., aes(x = x, y = y, color = dsprsn)) +
  scale_color_gradient(low = "green", high = "blue") +
  geom_point(alpha = 0.8) +
  coord_equal() +
  theme_bw()
